### 2017-01-31 2017mergingmerges/section/XX-Processes.tex
Work through introduction
start on concrete expression syntax

This section describes processes in detail.
We start with an informal explanation of processes before formally defining the syntax and dynamic semantics.

@@

\begin{code}
process (group)
     ins: file1
    outs: uniques
    heap: {first = True, last = 0, value = 0}
   label: L0
  blocks: L0 = pull file1   value              L1
          L1 = case (first || last /= value)   L2               L3
          L2 = push uniques value              L3{last = value, first = False}
          L3 = drop file1                      L0
\end{code}

@@

\begin{code}
process (group/merge)
     ins: file1 file2
    outs: uniques merged
    heap: {first = True, last, value_a, b}
   label: L0
  blocks: L0 = pull file1   value_a             L1
          L1 = case (first || last /= value_a)  L2    L3
          L2 = push uniques value_a             L3{last = value_a, first = False}
          L3 = pull file2 b                     C0

@@

          A0 = push merged  value_a             A1
          A1 = drop file1                       A2
          A2 = pull file1   value_a             A3
          A3 = case (first || last /= value_a)  A4    C0
          A4 = push uniques value_a             C0{last = value_a, first=False}

>>>>

% BL: Just start into the description.
%     Readers will work out what's coming by flipping through the paper themselves.
% This section describes processes in detail. We start with an informal explanation of processes before formally defining the syntax and dynamic semantics.

@@

\begin{code}
process (group)
     ins: file1
    outs: uniques
    heap: {first = True, last = 0, value = 0}
   label: L0
  blocks: L0 = pull file1   value               L1
          L1 = case (or first (last /= value))  L2               L3
          L2 = push uniques value               L3{last = value, first = False}
          L3 = drop file1                       L0
\end{code}

@@

\begin{code}
process (group/merge)
     ins: file1 file2
    outs: uniques merged
    heap: {first = True, last, value_a, b}
   label: L0
  blocks: L0 = pull file1   value_a               L1
          L1 = case (or first (last /= value_a))  L2    L3
          L2 = push uniques value_a               L3{last = value_a, first = False}
          L3 = pull file2 b                       C0

@@

          A0 = push merged  value_a               A1
          A1 = drop file1                         A2
          A2 = pull file1   value_a               A3
          A3 = case (or first (last /= value_a))  A4    C0
          A4 = push uniques value_a               C0{last = value_a, first=False}
